---
title: "Interpreting Model Output - Patrick Torralba"
author: "Patrick Torralba"
format: 
  html:
    theme: flatly
    fontsize: 0.8em
    code-fold: FALSE
    code-tools: TRUE
    code-copy: TRUE
    toc: TRUE
    toc-depth: 4
    smooth-scroll: TRUE
    embed-resources: TRUE
    fig-align: center
editor: visual
---

# Preliminary

```{r}
#| label: library-import
#| message: FALSE
#| warning: FALSE
#| echo: TRUE  

library(tidyverse)
library(tidymodels)
library(kableExtra)
library(stats)
library(broom)

gum <- read_csv("gumR2026.csv") |> 
  mutate(trtgroup = fct_relevel(trtgroup, "Placebo"))

```


# Questions

```{r}
#| label: q1
#| message: FALSE
#| warning: FALSE
#| echo: TRUE

## Continuous GLM

model_1 <- glm(
  mut3mos ~ trtgroup,
  family = gaussian(link = "identity"),
  data = gum
) 

summary(model_1)

kable(tidy(model_1, conf.int = TRUE),
      digits = 3)

```

## Answer 1
The treatment effect estimate is -1.326 (cfu/ml) and it has a 95% confidence interval of (-1.96 to -0.690). This effect is statistically significant (p-value < 0.05). 

The treatment effect has a slope of zero because the treatment effect doesnt depend on the baseline MS level.


```{r}
#| label: q2
#| message: FALSE
#| warning: FALSE
#| echo: TRUE

## Interaction Model

model_2 <- glm(
  mut3mos ~ trtgroup * mutpre,
  family = gaussian(link = "identity"),
  data = gum
) 

summary(model_2)

kable(tidy(model_2, conf.int = TRUE),
      digits = 3)


```

## Answer 2
The treatment effect estimate is -0.004 (cfu/ml) with a 95% confidence interval of (-0.826 to 0.818).

The mean model is E(Y) = B0 + B1(trtgroup) + B2(baseline) + B3(trtgroup x baseline)