---
title: "Assignment 0 - Patrick Torralba"
author: "Patrick Torralba"
format: 
  html:
    theme: flatly
    fontsize: 0.8em
    code-fold: FALSE
    code-tools: TRUE
    code-copy: TRUE
    toc: TRUE
    toc-depth: 4
    smooth-scroll: TRUE
    embed-resources: TRUE
    fig-align: center
editor: visual
---

#Library
```{r}
#| label: library
#| message: FALSE
#| warning: FALSE
#| echo: TRUE 

library(tidyverse) #clean data

```

#Import Data
```{r}
#| label: import
#| message: FALSE
#| warning: FALSE
#| echo: TRUE  

chicks <- read_csv("chicks.csv")

```

# Structure Review
```{r}
#| label: structure-review
#| message: FALSE
#| warning: FALSE
#| echo: TRUE  

obs <- nrow(chicks)

col <- ncol(chicks)

chicks_grouped <- chicks |> 
  group_by(Chick, Diet) |> 
  summarize(
    repeat_measurement = n())

```

** There were a total of 50 chicks studied and there were 12 repeated measurements per weight / time. There is missing data for some of the chicks. Some chicks like chick 16 only had 7 repeated measurements. **

# Outliers

To calculate the outliers we're going to do a boxplot.

```{r}
#| label: boxplot
#| message: FALSE
#| warning: FALSE
#| echo: TRUE  

ggplot(chicks, aes(y = weight)) +
  geom_boxplot() +
  labs(
    y = "Weight",
    title = "Chick Weight Distribution"
  )

boxplot.stats(chicks$weight)
```

** It looks like the chick weight outliers are chicks weighing over 318+ units.**


# Chick Graph
```{r}
#| label: graph
#| message: FALSE
#| warning: FALSE
#| echo: TRUE  

chicks |> 
  mutate(Diet = as.factor(Diet)) |> 
ggplot(aes(x = Time, y = weight, color = Diet)) +
  geom_point() +
  labs(x = "Time (Day)",
       y = "Weight",
       title = "Chick Weight by Time and Diet")

```

# Chick Stats

## Do Chicks' Weight Change over Time?

I think I should calculate the p-value for a linear regression model.

```{r}
#| label: stats-chick-weight-over-time
#| message: FALSE
#| warning: FALSE
#| echo: TRUE  

# calculate Linear Regression model

chick_model <- lm(weight ~ Time + Diet, data = chicks)
summary(chick_model)


## Convert to kable table for professionalism

library(kableExtra)
library(knitr)
library(broom)

chick_model_tidy <- tidy(chick_model, conf.int = TRUE)

## Format table
kable(
  chick_model_tidy,
  format = "html",
  digits = 3,
  caption = "Linear Regression Model: Chick Weight by Time and Diet",
)


```
** According to my model, yes there is significant statistical evidence to say that chicks' weight does change ver the time of the study. **

## Is there an effect of diet on weight change?

To determine if there's an effect of diet on weight change, I will conduct a One-way ANOVA
```{r}
#| label: diet-weight-change-stats
#| message: FALSE
#| warning: FALSE
#| echo: TRUE  

ANOVA_model <- aov(weight ~ Diet, data = chicks)

summary(ANOVA_model)
```

** Yes, there is statistically significant evidence to prove that diet affects chick weight. **